\documentclass{article}

\usepackage{fullpage}

\begin{document}

	\section{Methods}

		I have three ideas I have tried.
		In the first two I cluster on the data and then learn a function for each cluster.
		Then I try to do a linear combination of those functions to get a good output.
		In the final method I take the entire dataset and use a few known ranking algorithms to learn how to combine those.

		\subsection{Method One}

			In this method we perform logistic regression on each cluster and then learn how to combine the resulting models together.

			\begin{itemize}
				\item cluster data
				\item for each cluster use logistic regression to learn how to rank 
				\item Create a new data data using ranking functions to create a matrix of outputs.
				\item Learn coefficients for each algorithms output (linear and non-linear combinations) 
			\end{itemize}

		\subsection{Method Two}

			In this method we use a known learning to rank algorithm on each cluster and then learn how to combine the resulting models together.
			\begin{itemize}
				\item cluster data
				\item for each cluster use a known Ranking algorithm
				\item Create a new data data using ranking functions to create a matrix of outputs.
				\item Learn coefficients for each algorithms output (linear and non-linear combinations) 
			\end{itemize}

		\subsection{Method Three}

			In this method we perform learning to rank using multiple learners on the test data and then learn how to combine the models together. 

			\begin{itemize}
				\item For each ranking algorithm train on the entire data set
				\item Create a new data data using the outputs of each ranking functions
				\item Learn coefficients for each algorithms output (linear and non-linear combinations) 
			\end{itemize}

	\section{Combining}

		For combining I have two ideas: use logistic regression to learn the coefficients, use a weighted sceheme that penalizes outputs which are wrong.
		For our weighting scheme we apply the following algorithm
		
		\begin{itemize}
			\item  Let $C = <c_1,...,c_m>$
			\item  $c_j = \frac{1}{N} \sum_{i=1}^{N} \frac{x_{ij}}{({x_{ij}} - y_i)^2 + 0.00001}$
			\item  Normalize $C$
		\end{itemize}	

\end{document}
